### 2013-09-06 research/paper/results/results-2.3.tex
commit some modifications...

 The data presented in \ref{fig:uncollapsed_data} for various damping ratios ,$\zeta$, can be collapsed into a single line for a for a particular force characteristic curve (i.e $C_y$ vs $\theta$ curve)  curve could be obtained for the velocity amplitude  and power were plotted as a function of  non dimensionalised  damping constant $c$ 
(Fig \ref{fig:collpased_data} (a),(b),(c) and (d)). Fig.\ref{fig:time_hostory_velocity_same_power} clearly shows that a similar velocity amplitude could be obtained for a given damping factor provided that the small fluctuations are disregarded.

>>>>

 The data presented in \ref{fig:uncollapsed_data} for various damping ratios ,$\zeta$, can be collapsed into a single line for a for a particular force characteristic curve (i.e $C_y$ vs $\theta$ curve)  curve could be obtained for the velocity amplitude  and power were plotted as a function of  non dimensionalised  damping constant $c$ 
(Fig \ref{fig:collpased_data} (a),(b),(c) and (d)).  This further emphasizes that the galloping system is not frequency dependent. It is possible to obtain a different similar power output at different values of \usta when the damping constant \hilight{...}, is kept fixed. An example of this case, as shown in Fig.\ref{fig:time_hostory_velocity_same_power}, clearly show that this is a result of similar velocity amplitudes between cases if one were to disragard the high frequencies due to shedding. As mentioned earlier, it is the transverse velocity that determines the energy provided by the fluid forcing and the mechanical damping.
